---
title: "hw06-Ninadh"
author: "Ninadh"
date: "November 6, 2018"
output: html_document
---

This is the first assignment of STAT 547M (despite it being named Homework 06).
The task is to complete two of the six topics.

Let's load up!

```{r setup, include=FALSE}
library(gapminder)
library(tidyverse)
library(stringr)
library(knitr)
library(repurrrsive)
library(testthat)
```

Task 2: Write function

Write one (or more) functions that do something useful to pieces of the Gapminder or Singer data. It is logical to think about computing on the mini-data frames corresponding to the data for each specific country, location, year, band, album, … This would pair well with the prompt below about working with a nested data frame, as you could apply your function there. Make it something you can’t easily do with built-in functions. 

Make it something that’s not trivial to do with the simple dplyr verbs. The linear regression function presented here is a good starting point. You could generalize that to do quadratic regression (include a squared term) or use robust regression, using `MASS::rlm()` or `robustbase::lmrob()`.

```{r}
#lets take a look at the dataframe 
gapminder 
```

Let me filter my country, Bangladesh

```{r}
gapminder %>%
  filter(country == "Bangladesh") %>%
  kta
```

