---
title: "hw06-Ninadh"
author: "Ninadh"
date: "November 6, 2018"
output: github_document
---

This is the first assignment of STAT 547M (despite it being named Homework 06).
The task is to complete two of the six topics.

Let's load up!

```{r setup, include=FALSE}
library(gapminder)
library(tidyverse)
library(stringr)
library(knitr)
library(repurrrsive)
library(testthat)
library(dplyr)
library(broom)
```

Task 2: Write function

Write one (or more) functions that do something useful to pieces of the Gapminder or Singer data. It is logical to think about computing on the mini-data frames corresponding to the data for each specific country, location, year, band, album, … This would pair well with the prompt below about working with a nested data frame, as you could apply your function there. Make it something you can’t easily do with built-in functions. 

Make it something that’s not trivial to do with the simple dplyr verbs. The linear regression function presented here is a good starting point. You could generalize that to do quadratic regression (include a squared term) or use robust regression, using `MASS::rlm()` or `robustbase::lmrob()`.

```{r}
#lets take a look at the dataframe 
gapminder 
```

Let me filter my country, Bangladesh

```{r}
gapminder %>%
  filter(country == "Bangladesh") %>%
  knitr::kable()
```

To use the linear regression function for the dataframe, lets use a variable for the dataset and plot it.

```{r}
gap_ban <- (gapminder %>%
  filter(country == "Bangladesh"))
```


```{r}
ggplot(gap_ban, aes(x=year, y= lifeExp)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) 
```

I had no idea that it wound be such a good graph. the linear regression is a good formula as most of the dots fall on the line. 

to use linear regression for the above data:

```{r}
lm(formula = lifeExp ~ year, data = gap_ban)
coef(lm(formula = lifeExp ~ year, data = gap_ban))
```

Let's now try the quadratic function on the same data

```{r}
gap_ban_quad <- lm(formula = lifeExp ~ I(year) + I(year^2), data = gap_ban)
coef(gap_ban_quad)
```

I always like graphical presentaion of my data.

```{r}
ggplot(gap_ban, aes(x=year, y=lifeExp)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x + I(x^2), se = FALSE)
```

Well, the quadraic formula is a good fit as well. 



Task 06: Work with a nested data frame

# to make my life easier.

Create a nested data frame and map a function over the list column holding the nested data. Use list extraction or other functions to pull interesting information out of these results and work your way back to a simple data frame you can visualize and explore.

# nesting the dataframe by country and continent (following Jenny's footsteps)

```{r}
gapminder %>%
  group_by(country, continent) %>%
  nest()
```

# assigning the dataframe

```{r}
gap_nest <- (gapminder %>%
  group_by(country, continent) %>%
  nest())
```

# inspected the dataframe with "gap_nest %>% View()"


# data for Bangladesh by [9]

```{r}
gap_nest[[9, "data"]]
```



# fitting the data of life-expectancy by year in quadratic model

```{r}
quad_model <- function(data) {
  lm(formula = lifeExp ~ I(year) + I(year^2), data=gap_nest[[9, "data"]])
}
```


# does the function work?

```{r}
quad_model(gap_nest$lifeExp)
```

# yeahhhh it works.

Trying the robust model now

```{r}
robust_model <- function(data) {
  MASS::rlm(formula = lifeExp ~ I(year) + I(year^2), data=gap_nest[[9, "data"]])
}
```

# does it work?

```{r}
robust_model(gap_nest$lifeExp)
```

# to double check that same result is returned with another formula

```{r}
ban_le_yr <- function(df) {
  lm(lifeExp ~ I(year) + I(year^2), data = df)
}
ban_le_yr(gap_nested[[9, "data"]])
```

the values are slightly different!

# lets check whether it "fits" for Afganistan, Albania and Algeria

```{r}
map(gap_nest$data[1:3], ban_le_yr)
```

```{r}
fits <- map(gap_nest$data[1:3], ban_le_yr)
fits
```

# using broom to tidy up the data

```{r}
(gap_nest2 <- gap_nest %>% 
   mutate(fit = map(data, ban_le_yr)))
```

# data of Bangladesh in one glance

```{r}
tidy(gap_nest2$fit[[9]])
```

```{r}
gap_nest2 %>% 
  mutate(tidy = map(fit, tidy))
```



```{r}
gap_nest2 %>% 
  mutate(tidy = map(fit, tidy)) %>%
  select(continent, country, tidy)
```

```{r}
gap_nest2 %>% 
  mutate(tidy = map(fit, tidy)) %>%
  select(continent, country, tidy) %>%
  unnest(tidy)
```

```{r}
gap_coef <- gap_nest2 %>% 
  mutate(tidy = map(fit, tidy)) %>%
  select(continent, country, tidy) %>%
  unnest(tidy)
```

# A tabular presentation of the data
 
```{r}
gap_coef %>%
  filter(continent == "Asia") %>%
knitr::kable()
```

